---
title: "20201012-p8122_hw2_jsg2145"
author: "Jared Garfinkel"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Read in data

```{r, results = "hide"}
data = read_csv("./data/light.csv") %>% 
  janitor::clean_names()

data
```

# Problem 1

```{r}
data %>% 
  ggplot(aes(x = light, y = bm_gain, fill = light)) +
  geom_boxplot(alpha = 0.7)
```

# Problem 2

Assuming DM = darkness, LD = dim, and LL = bright

### subset the data

```{r}
df = data %>% 
  filter(light %in% c("DM", "LL"))
```

# Problem 3

Recode the variables and rename them for ease of use.

```{r}
df = df %>% 
  mutate(light = recode(light, 
                        "DM" = "0",
                        "LL" = "1")) %>% 
  rename("tr" = light,
         "y" = bm_gain)
```

We will need the estimand and the sampling variance to evaluate the causal effects of light at night on weight gain in mice for Neyman's approach, or the observed outcomes, the treatment group assignments, and the covariates, for Fisher's approach.

# Problem 4

$T_{obs} = \frac{\sum_{i=1}^{n}{A_iY_{1i}}}{N_1} - \frac{\sum_{i=1}^{n}(1-A_i)Y_{0i}}{N_0}$

```{r}
t_obs = df %>% 
  summarize(t_obs = sum(y*(tr==1)/sum(tr==1) - y*(tr==0)/sum(tr==0)))
```

T_obs is `r pull(t_obs, t_obs)`.

# Problem 5

```{r}
amat = perm::chooseMatrix(19, 10)

nrow(amat)
```
There are 92378 different ways to arrange the A matrix.

# Problem 6

The sharp null hypothesis of no difference is that for each observation there is no treatment effect. 

That is: $H_0: \tau_i = Y_{0i} - Y_{1i} = 0$

```{r}
atilde = amat[1,]

t_stat = df %>% 
  bind_cols(atilde) %>%
  rename("atilde" = "...10") %>% 
  summarize(t_stat = sum(y*(atilde==1)/sum(atilde==1)) - sum(y*(atilde==0)/sum(atilde==0)))
```
The t-statistic under the sharp null hypothesis is `r pull(t_stat, t_stat)`


# Problem 7

```{r, cache = TRUE}
rdist = vector(mode = "list", length = nrow(amat))
atilde = NULL
for (i in 1:nrow(amat)) {
  atilde[[i]] = amat[i,] %>% 
    tibble()
  rdist[[i]] = df %>%
    bind_cols(atilde[i]) %>% 
    rename("atilde" = ".") %>% 
    summarize(rdist = sum(y*(atilde==1)/sum(atilde==1)) - sum(y*(atilde==0)/sum(atilde==0)))
}

rdist = bind_rows(rdist)
```


```{r}
rdist %>% 
  pull(rdist) %>% 
  hist()
abline(v = pull(t_obs, t_obs))
```

```{r}
p <- mean(rdist >= pull(t_obs, t_obs))
p
```